City-GAN: Learning architectural styles using a custom Conditional GAN architecture

### 2019-07-01 paper.tex
Add missing figures

We present two new datasets for \glspl{gan}: both datasets consist of thousands of images of facades of buildings in various cities. Each image also has a label, which indicates the city of the building depicted.

@@

@@

\end{itemize}
\begin{figure}[h]
\includegraphics[width=0.49\columnwidth{}]{"paris/1 Place de Mexico, 75016".jpg}%
\hspace{0.015\columnwidth}%
\includegraphics[width=0.49\columnwidth{}]{"paris/1 Port de la Bourdonnais, 75007".jpg}
\caption{Two examples of pictures that we did not include in our dataset: on the left image there are gaps in the facades, the right one is anomalous (not a facade).}
\label{fig:example_invalid}
\end{figure}

>>>>

We present one new dataset for \glspl{gan}: The dataset consists of thousands of images of facades of buildings in various cities. Each image also has a label, which indicates the city of the building depicted.

@@

All our code and the dataset we used are available at \url{https://github.com/muxamilian/city-gan}.

@@

\end{itemize}
\begin{figure}[h]
\includegraphics[width=0.49\columnwidth{}]{"figures/examples/1 Place de Mexico, 75016".jpg}%
\hspace{0.015\columnwidth}%
\includegraphics[width=0.49\columnwidth{}]{"figures/examples/1 Port de la Bourdonnais, 75007".jpg}
\caption{Two examples of pictures that we did not include in our dataset: on the left image there are gaps in the facades, the right one is anomalous (not a facade).}
\label{fig:example_invalid}
\end{figure}
